---
title: "HW04_XU ZHANG_DSO545"
author: "Xu Zhang"
date: "March 5, 2018"
output:
  word_document: default
  html_document: default
---

```{r }
setwd("C:/Users/Xu Zhang/Desktop/DSO545")
load("hubwaytrip2012.rda")
library(lubridate)
library(dplyr)
library(ggplot2)
```

1.	Use functions from dplyr and lubridate to summarise by Day and Start Time (Hour of the day) of bike rental usage. Save your new dataframe in a variable called trips2012Time, and output head(trips2012Time) to show the first few observations of the new dataframe. (Make sure to set the timezone to "EST")

```{r }
trips2012$start_date=mdy_hm(trips2012$start_date)
trips2012$start_date=force_tz(trips2012$start_date,"EST")
trips2012Time=trips2012 %>%
  mutate(Day=wday(start_date,label=TRUE,abbr=FALSE),
            Start_time=hour(start_date)) %>%
  group_by(Day,Start_time) %>%
  summarise(count=n())
head(trips2012Time)

```

2.	Create the following heatmap , use color #e5f5e0 and #31a354. Summarise what you see.

```{r , echo=TRUE}
ggplot(trips2012Time,aes(x=Day,y=Start_time,fill=count))+
  geom_tile()+
  scale_fill_gradient(low = "#e5f5e0",high ="#31a354",guide = FALSE)+
  labs(title="Heatmap of Hubway Bike Rental Day V.S. Hour",x="",y="Hour of the Day")+
  scale_y_continuous(breaks = seq(0,24,1))
```

People rent bike more on weekdays than on weekends. People rent bike more on 7:00 AM to 9:00 AM and 4:00 PM to 6:00 in a day than other time.
